Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-03-03 src/tex/ms.tex
chip definition

Besides source inclination, the effect of birefringence can be (partially) degenerate with other parameters---most notably, precession, as we find in Sec.~\ref{sec:Results}.
Indeed, under the right conditions, the frequency-dependent amplification or dampening of polarizations caused by $\kappa$ can be effectively absorbed by changes in intrinsic parameters, like the spins;
in that case, the degeneracy with inclination may appear even for lighter \acp{BBH} (although usually to a lesser degree than heavy binaries).
We chart some of these degeneracies as part of the results we present in Sec.~\ref{sec:Results}.
% In particular, we find that, under certain conditions, the frequency-dependent birefringence of Eq.~\eqref{eq:waveform_modification} can mimic the time-dependent amplitude modulation expected from a precessing system.

>>>>

Besides source inclination, the effect of birefringence can be (partially) degenerate with other parameters---most notably, precession, as we find in Sec.~\ref{sec:Results}.
Indeed, under the right conditions, the frequency-dependent amplification or dampening of polarizations caused by $\kappa$ can be effectively absorbed by changes in intrinsic parameters, like the spins;
in that case, the degeneracy with inclination may appear even for lighter \acp{BBH} (although usually to a lesser degree than heavy binaries).
Specifically, the interplay between birefringence and precession will manifest in the posterior of the precessing spin parameter $\chi_p$, defined as \cite{Schmidt:2014iyl}
\begin{equation}
\chi_p \equiv \max\left\{ ||\vec{\chi}_{1\perp}||,\, k ||\vec{\chi}_{2\perp}||\right\} ,
\end{equation}
where $\vec{\chi}_{i\perp}$ are the projections of the dimensionless spin vectors onto the orbital plane at a reference time, and $k \equiv q\left(4 q +3\right) / \left(4 + 3q\right)$ for a mass ratio $q \equiv m_2/m_1 \leq 1$.
We chart this and other degeneracies as part of the results we present in Sec.~\ref{sec:Results}.

% In particular, we find that, under certain conditions, the frequency-dependent birefringence of Eq.~\eqref{eq:waveform_modification} can mimic the time-dependent amplitude modulation expected from a precessing system.
